\documentclass{article}

\usepackage[a4paper, total={6.5in, 9.2in}]{geometry}
\usepackage{changepage}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tocloft}

\setcounter{tocdepth}{1} % Show sections

\titleformat*{\subsubsection}{\rm}
\titleformat*{\subsection}{\rm}
\titleformat*{\section}{\rm}

\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    linkbordercolor=red,
    urlcolor=black
}

\def\contentsname{\empty}

\newenvironment{subs}
  {\adjustwidth{2em}{0pt}}
  {\endadjustwidth}

\renewcommand\cfttoctitlefont{\hfill\Large\bfseries}
\renewcommand\cftaftertoctitle{\hfill\mbox{}}

\setcounter{tocdepth}{1}
 
\begin{document}
\begin{center}
{\Large\bf CONSTITUTION OF ADELAIDE BLOCKCHAIN \par}
\end{center}
\vspace{10mm}

{\large\bf TABLE OF CONTENTS\par}
\hrulefill

\tableofcontents
\clearpage

{\large\bf NAME OF THE ASSOCIATION\par}
\hrulefill
\section{Name}
\begin{subs}
\subsection{The name of the Association is Adelaide Blockchain, referred to herein as (``the Association'').}
\end{subs}

\vspace{5mm}
{\large\bf OBJECTS\par}
\hrulefill
\vspace{5mm}

\section{Objects of the Association}
\begin{subs}
\subsection{Are to;}
\begin{subs}
\subsubsection{To represent and promote the interests of all members within the Association;}
\subsubsection{To promote and facilitate interaction between the Association, its members, and the wider persons whose aims and interests align with that of the Association;}
\subsubsection{To promote and facilitate open forums to engage members and the broader community referred to in clause 2.1.2;}
\subsubsection{To promote and facilitate academic, social and vocational opportunities for members.}
\end{subs}

\subsection{Subject to and without limiting the objectives provided for in clause 2 above, the association will pursue its objectives through activities including but not limited to:}

\begin{subs}
\subsubsection{Organising and facilitating educational events for members and students;}
\subsubsection{Providing a foundation and support network to empower members to work on practical projects and research and development in order to further their skills and develop ties with like-minded individuals;}
\subsubsection{Promoting and advocating for the interests of the Association's members to any relevant organisation;}
\subsubsection{Publishing and making generally available information in relation to careers, education and other matters of general interest to members;}
\subsubsection{Organising and facilitating social events for members and students;}
\subsubsection{Entering into any business arrangements, attracting sponsorship, strategic partnerships and otherwise raising money considered to be necessary for the achievement and conduct of the Association's objectives and activities.}
\end{subs}
\end{subs}

\vspace{5mm}
{\large\bf DEFINITIONS\par}
\hrulefill
\vspace{5mm}

\section{Definitions}
\begin{subs}
\subsection{Unless the contrary intention appears, the following rules of interpretation apply and the following terms shall have the meanings as set out below:}
\begin{subs}
\subsubsection{``Act'' means the \textit{Associations Incorporation Act 1985 (SA)} and any relevant regulations.}
\subsubsection{``The Board'' means the Board of management, comprised of the Directors of the Association}
\subsubsection{``By-Law'' means a By-Law adopted by the Association.}
\newpage

\subsubsection{``Constitution'' means this constitution.}
\subsubsection{``Director'' means a member of the Board.}
\subsubsection{``Financial Year'' means the period beginning on 1 July of each calendar year and ending on 30 June of the following calendar year.}
\subsubsection{``General Meeting'' means a General Meeting of members of the Association convened in accordance of this Constitution.}
\subsubsection{``Member'' means a person under this constitution who is a member of the Association.}
\subsubsection{``Ordinary Resolution'' means a resolution passed by a simple majority at any relevant meeting.} 
\subsubsection{``Special Resolution'' means a resolution passed at a duly convened meeting of the members of the Association if:-}
\begin{subs}
\begin{itemize}
\item[(i)] at least 21 days  written notice specifying the intention to propose the resolution as a special resolution has been given to all members of the Association; and
\item[(ii)] it is passed at at a meeting referred to in this paragraph by a majority of not less then three-quarters of such members of the Association as, being entitled to do so, vote in person or where proxies are allowed, by proxy, at that meeting.
\end{itemize}
\end{subs}
\subsubsection{``Student'' means a person enrolled at a recognised secondary or tertiary Australian education institution for the relevant time.}
\subsubsection{``Term'' means the period that Directors are in Office between Annual General Meetings.}
\end{subs}
\subsection{Headings are for convenience only and do not affect the interpretation of any clauses of this constitution.}
\subsection{Any reference to the singular includes the plural.}
\subsection{Any reference to days will be calendar days.}
\subsection{Any reference to any amount in dollars will be Australian dollars.}
\subsection{Where a word or phrase is defined its other grammatical forms have a corresponding meaning.}
\end{subs}

\section{Relationship to By-Laws}
\begin{subs}
\subsection{In the event of an inconsistency between this constitution and any By-Laws of the Association, this Constitution prevails to the extent of the inconsistency.}
\end{subs}
\newpage

{\large\bf POWERS OF THE ASSOCIATION\par}
\hrulefill

\section{The Powers of the Association}
\begin{subs}
\subsection{Shall have all the powers conferred by section 25 of the Act. In addition to and without limiting the powers of the Association contained in the Act, the Association shall have the following powers for the purpose of carrying out the objects of the Association:}
\begin{subs}
\subsubsection{Collect funds for the purpose of enabling the objects of the Association to be carried out; and}
\subsubsection{Appoint agents to transact any business of the Association on it's behalf; and}
\subsubsection{Enter into any other contract it considers necessary or desirable; and}
\subsubsection{For the purpose of carrying out the objects of the Association, accept gift donations and legacies made by or bequeathed by members or other persons; and}
\subsubsection{To do all such other lawful things as are conducive or incidental to the attainment of any of the objects of the Association.}
\end{subs}
\end{subs}

\vspace{5mm}
{\large\bf MEMBERSHIP\par}
\hrulefill
\vspace{5mm}

\section{Members of the Association}
\begin{subs}
\subsection{General Membership}

\begin{subs}
\subsubsection{Subject to the terms of this Constitution, any individual who indicates a desire to become a member of the Association and aligns with the Association's objects may be eligible for membership.}
\subsubsection{A General Member is a voting member of the Association.}
\end{subs}
\end{subs}

\section{Subscriptions}
\begin{subs}
\subsection{All Member subscriptions shall be free.}
\subsection{All General Memberships shall last indefinitely unless otherwise determined by the Board; or if such member resigns as per clause 8.}
\end{subs}

\section{Resignations}
\begin{subs}
\subsection{A member may resign their membership at any time by notice in writing (digital or otherwise) to the President of the Association.}
\end{subs}
 

\section{Expulsion of a member}
\begin{subs}
\subsection{Subject to giving a member an opportunity to be heard or to make a written submission, the Board may resolve to expel a member upon charge of misconduct detrimental to the interests of the Association.}
\subsection{Particulars of the charge shall be communicated to the member at least 31 days before the meeting of the Board at which the matter will be determined.}
\subsection{The determination of the Board shall be communicated  to the member, and in the event of an adverse determination shall, subject to clause 9.4 below, cease to be a member 14 days after the Board has communicated its determination to the member.}
\newpage

\subsection{It shall be open to the member to appeal the expulsion to the Association at a General Meeting. The intention to appeal shall be communicated to the President of the Association within 14 days after the determination of the Board has been communicated to the member.}
\subsection{In the event of an appeal under clause 9.4 above, the appellant's membership of the Association shall not be terminated unless the determination of the Board to expel the member is upheld by the members of the Association in the General Meeting after the appellant has been heard by the members of the Association, and in such event the membership will be terminated at the date of the General Meeting at which the determination of the Board is upheld.}
\end{subs}

\section{Register of Members}
\begin{subs}
\subsection{A ``register of members'' shall be kept by the Secretary.}
\subsection{The ``register of members'' must contain the following information about each member:}
\begin{subs}
\subsubsection{Their Name; and}
\subsubsection{Their Email Address; and}
\subsubsection{The date of membership admission to the Association.}
\subsubsection{The date of the reason(s) for termination of membership if applicable.}
\end{subs}
\end{subs}

\vspace{5mm}
{\large\bf THE BOARD\par}
\hrulefill
\vspace{5mm}

\section{Composition of the Board}
\begin{subs}
\subsection{The affairs of the Association shall be governed by a board (in this constitution called ''the Board'') which shall consist of a maximum of 9 persons (``Directors''), each with voting rights and including at least 1 person from the following categories;}
\begin{subs}
\subsubsection{A Head of Operations; and}
\subsubsection{A Head of Marketing; and}
\subsubsection{A Head of Research and Development; and}
\subsubsection{No more then 6 other Directors as seen fit by the Board.}
\end{subs}
\end{subs}

\section{Appointment of the Board}
\begin{subs}
\subsection{A Director shall be a natural person.}
\subsection{For a person to be eligible for election as a Director, he or she must deliver a nomination to the President of the Association at least 21 days before the Annual General Meeting. It is a requirement that nominees must be a member of the Association.}
\begin{subs}
\subsubsection{The President is required to present all nominations to the Board. Upon the Boards discretion through Ordinary Resolution, the Board shall pick from the nominations any nominees they believe adequate for Director positions, who will then be up for election at the Annual General Meeting.}
\end{subs}
\subsection{The first Board of the Association shall be comprised of such persons who hold office prior to incorporation. The first Board shall hold office until the first Annual General Meeting after incorporation.}
\newpage

\subsection{At the first Annual General Meeting, every Director of the Board shall be up for re-election.}
\subsection{No Director may be in the Board for more then 1 term without re-election.}
\end{subs}

\section{Officers of the Board and their Duties}
\begin{subs}
\subsection{The Directors of the Board shall elect from amongst their number the following Officers (who together form the Executive Committee of the
Board) and their role is determined by the By-Laws of the constitution adopted by the Association.}
\begin{subs}
\subsubsection{A President;}
\subsubsection{A Treasurer;}
\subsubsection{A Secretary;}

\section{Retirement of the Board}
\begin{subs}
\subsection{The Board shall at a meeting of the Board held not less then twenty one days prior to the Annual General Meeting in each year resolve the number of positions on the Board for which nominations shall be called.}
\subsection{All Directors whose terms of Office end at the Annual General Meeting shall by default retire.}
\subsection{All elected Directors, nominated Directors and ex-officio Directors of the Board shall remain in Office until the conclusion of the meeting at which their successors are elected, nominated or appointed as the case may be.}
\end{subs}

\section{Quorum}
\begin{subs}
\begin{subs}
\subsection{At any Board meeting fifty percent or more Directors of the Board must be present to constitute a quorum.}

\end{subs}
\end{subs}

\section{Vacancies}
\begin{subs}
\subsection{An Office of the Board will be vacant where no person holds the position of the Office, and an Office will become vacant where:}
\begin{subs}
\subsubsection{The person holding the position of the Office ceases to hold the Office for any reason;}
\subsubsection{The position of the Office is not filled following a duly constituted election; or}
\subsubsection{Becomes vacant for any other reason.}
\end{subs}
\subsection{In the event that an office of the Board is vacant the Board may: }
\begin{subs}
\subsubsection{Appoint any person eligible for election to an office to the vacant office by Ordinary Resolution; or}
\subsubsection{Hold a by-election to fill the vacant office by Special Resolution; or}
\subsubsection{Take no action.}
\end{subs}
\end{subs}
\newpage

\section{Disqualification of Directors}
\begin{subs}
\subsection{The Office of a Director becomes vacant if a Director is:}
\begin{subs}
\subsubsection{Permanently incapacitated by ill health;}
\subsubsection{Disqualified from being a Director by the Act;}
\subsubsection{Expelled as a Director under this Constitution or it's By-Laws;}
\subsubsection{Resigns in writing to the rest of the Board;}
\subsubsection{Absent without apology from more than four meetings in a financial year.}
\end{subs}
\end{subs}

\section{Conflict of Interest}
\begin{subs}
\subsection{An Director of The Board having a direct or indirect pecuniary interest in a contract or proposed contract with the Association must disclose the nature and extent thereof that interest to the Board as required by the Act.}
\end{subs}

\section{Powers of The Board}
\begin{subs}
\subsection{The Board shall have ultimate responsibility of management and control of the Association, in addition to any powers and authorities conferred by this constitution, may exercise all such powers and do all such things as are within the objects of the Association, and are not by the Act or by these rules required to be done by the Association in a general meeting.}
\subsection{In addition to its other powers, and without affecting the generality of clause 19.1 of this constitution, the Board shall have the following powers:}
\begin{subs}
\subsubsection{To expend the funds of the Association in such a manner it considers most beneficial to achieve the objects of the Association;}
\subsubsection{To enter contracts on behalf of the Association;}
\subsubsection{To enter into any lawful transaction or to do any other lawful things incidental or conductive to the attainment of the objects or the execution of the powers of the Association.}
\subsection{The Board shall have the authority to interpret the meaning of this constitution and any other matter relating to the affairs of the Association in which this constitution is silent.}
\end{subs}
\end{subs}

\section{The President}
\begin{subs}
\subsection{The President, in addition to the duties outlined in this constitution and it’s By-Laws, shall be subject to the directions of The Board and of the constitution be responsible for the management of the Association.}
\begin{subs}
\subsubsection{The President, or it’s nominee, shall attend all Special, General and ordinary board meetings of the Association.}
\subsubsection{The President shall be the Public Officer of the Association and such duties shall be required by the Act, unless the Board shall otherwise resolve.}
\subsubsection{The President shall ensure all decisions by the Board are in adherence to the Constitution and its By-Laws, and any other relevant Australian Laws.}
\end{subs}
\end{subs}

\section{Proceedings of the Board}
\begin{subs}
\subsection{The Board shall not meet less then twelve occasions per calender year in intervals no greater then eight weeks between each meeting and at other times deemed necessary. The Board may adjourn and otherwise regulate its meetings as it sees fit.}
\subsection{Questions that arise from any meetings shall be resolved by Ordinary Resolution.}
\end{subs}
\newpage

\section{Indemnities}
\begin{subs}
\subsection{The Association shall indemnify and hold Officers harmless for all actions, costs, expenses, losses and demands incurred where the Officer or Officers have:}
\begin{subs}
\subsubsection{Acted in their capacity as an Officer;}
\subsubsection{Acted within the scope of their duties or with the approval of an ordinary motion of the Board;}
\subsubsection{Acted with the approval of the Board where required under this constitution, any relevant By-Law made under this constitution or any convention of the Board;}
\subsubsection{Acted in good faith;}
\subsection{Not acted (or continued to act) in breach of any law; and}
\subsection{Not acted (or continued to act) with negligence.}
\end{subs}
\end{subs}

\section{Committees of The Board}
\begin{subs}
\subsection{From time to time the Board may appoint any Committees as it sees fit in order to execute any such duties that will be required to further the Association's purpose.}
\subsection{The members of any such Committee shall remain in office for such period at the Board's pleasure, which it may determine from time to time.}
\subsection{Any Committee appointed by the Board shall be subject to the direction and control of the board.}
\end{subs}

\section{Minutes}
\begin{subs}
\subsection{The Secretary must prepare or cause to be prepared minutes of all business before all meetings of the Association.}
\subsection{Minutes shall be kept in the form as deemed necessary and appropriate by the Board and as required by the Act.}
\subsection{Minutes of meetings of the Board must be confirmed by the Board at the subsequent meeting of The Board.}
\end{subs}

\vspace{5mm}
{\large\bf GENERAL MEETINGS\par}
\hrulefill
\vspace{5mm}

\section{Annual General Meeting}
\begin{subs}
\subsection{The Association will convene the Annual General Meeting between February and November every calender year.}
\subsection{The business of the Annual General Meeting will include the following:}
\begin{subs}
\subsubsection{Confirmation of the minutes of the previous Annual General Meeting and of any Special General Meeting held since that meeting.}
\subsubsection{Receiving a report from each of the Directors of the Board;}
\subsubsection{Receiving statements of the financial affairs of the Association for the previous Financial Year by the Treasurer; and}
\subsubsection{Any other business as deemed necessary and appropriate.}
\end{subs}
\subsection{The President must provide notice of the Annual General Meeting to all members of the Association no later than 21 calendar days prior to the Annual General Meeting.}
\end{subs}
\newpage

\section{Special General Meeting}
\begin{subs}
\subsection{There shall be such other general meetings of the Association as the Board may from time to time determine.}
\subsection{The Board shall convene a Special General Meeting of the Association upon a requisition in writing under the hands of not fewer then ten voting Members or five percent of the members (whichever is more) of the Association.}
\subsection{Such requisition shall clearly and fully express the intended business of the meeting to be called.}
\subsection{Upon such requisition being so served the Board shall forthwith proceed to convene a Special General Meeting to be held at such time and place as it shall think fit not being more then 31 days after the service of such requisition setting out the business to be discussed.}
\subsubsection{If a Special General Meeting is not convened within 31 days, as required by clauses 26.2 and 26.4, the requisitionists, or at least 50 percent of their number, may convene a Special General Meeting. Such a meeting shall be convened in the same manner as nearly as practical as a meeting convened by the Board, and for this purpose the Board shall ensure that the requisitionists are supplied free of charge with particulars of the members entitled to receive a notice of meeting. The reasonable expenses of convening and conducting such a meeting shall be borne by the association.}
\end{subs}

\section{Notice of General Meetings}
\begin{subs}
\subsection{Subject to clause 27.2, at least 14 days notice of any general meeting shall be given to members. The notice shall set out where and when the meeting will be held, and particulars of the nature and order of the business to be transacted at the meeting.}
\subsection{Notice of a meeting at which a special resolution is to be proposed shall be given at least 21 days prior to the date of the meeting.}
\subsection{A notice maybe given by the Association to any member by serving the member with the notice personally, or by sending it through email appearing in the register of members.}

\subsection{Notice of any meeting required under this constitution must include:}
\begin{subs}
\subsubsection{The location of the meeting;}

\subsubsection{The beginning time of the meeting;}
\subsubsection{The particulars and order of business to be considered by the meeting.}
\end{subs}
\end{subs}

\section{Proceeding of General Meetings}
\begin{subs}
\subsection{Ten members or five percent of all members of the Association (whichever is larger) present personally or by proxy constitute a quorum of the transaction of business at any general meeting.}
\subsection{If within 30 minutes after the time appointed for the meeting a quorum of members is not present, a meeting convened upon the requisition of members shall lapse. In any other case, the meeting shall stand adjourned to any other day decided upon by the Board within two weeks of the general meeting and if at such adjourned meeting a quorum is not present within 30 minutes of the time appointed for the meeting the members present shall form a quorum.}
\end{subs}

\section{Voting at General Meetings}
\begin{subs}
\subsection{Subject to these rules, every member of the Association has only one vote at a meeting of the Association.}
\subsection{Subject to these rules, a question for decision at a general meeting, other then a special resolution, must be determined by a majority of members who vote in person or, where proxies are allowed, by proxy, at the meeting.}
\newpage

\subsection{Unless a poll is demanded by at least five members, a question for decision at a general meeting must be shown by a show of hands.}
\end{subs}

\section{Poll at General Meetings}
\begin{subs}
\subsection{If a poll is demanded by at least five members, it must be conducted in a manner specified by the person presiding and the result of the poll is the resolution of the meeting on that question.}
\subsection{A poll demanded for the election of a person presiding or on a question of adjournment must be taken immediately, but any other poll maybe conducted at any time before the close of the meeting.}
\end{subs}

\section{Special and Ordinary Resolutions}
\begin{subs}
\subsection{A Special Resolution is as defined in this constitution.}
\subsection{An Ordinary Resolution is as defined in this constitution.}
\end{subs}

\vspace{5mm}
{\large\bf PROXY\par}
\hrulefill
\vspace{5mm}

\section{Proxies}
\begin{subs}
\subsection{A member shall be entitled to appoint in writing a natural person who is also a member of the association to be their proxy, and attend and vote at any general meeting of the Association.}
\end{subs}

\vspace{5mm}
{\large\bf FINANCE AND ADMINISTRATION\par}
\hrulefill
\vspace{5mm}

\section{Prohibition against securing profits for members}
\begin{subs}
\subsection{The income, assets and capital of the Association shall be applied exclusively to the promotion of its objects and no portion shall be paid or distributed directly or indirectly to members or their associate except as bona fide remuneration for services rendered or expenses incurred on behalf of the Association.}
\end{subs}


\section{Accounts}
\begin{subs}
\subsection{The Association shall keep and retain such accounting records as are necessary to correctly record and explain the financial transactions and financial positions of the Association in accordance with the Act.}
\subsection{The Treasurer shall make the financial statements available for any inspection by any member upon request.}
\subsection{The Accounts, the Board's statement and the Board's Report, shall be laid before the members at the Annual General Meeting.}
\end{subs}

\section{Banking and Cryptocurrency accounts}
\begin{subs}
\subsection{The Association will hold fiat accounts and cryptocurrency wallets with any financial institution or blockchain as deemed necessary, respectively, in name of the Association from time to time by determination of the Board, which must include at least:}
\begin{subs}
\subsubsection{A general funds account;}
\subsubsection{A cryptocurrency exchange account;}
\newpage

\subsubsection{A hardware or other suitable cryptocurrency wallet;}
\end{subs}
\subsection{When donations and sponsorship funds are received in a foreign fiat or cryptocurrency they are to be withdrawn and transferred back to Australian Dollars within 24 hours of receipt.}
\subsection{All donations, sponsorship or other, received by cryptocurrency must do so through cryptocurrency wallets where the Association has full control of the wallets private keys.}
\end{subs}

\begin{subs}
\subsection{The funds of the Association may only be appropriated:}
\begin{subs}
\subsubsection{By Ordinary Resolution of the Board; or}
\subsubsection{In accordance with a By-Law adopted by the Association for the purpose of providing for the appropriation of funds of the Association.}
\end{subs}
\end{subs}

\vspace{5mm}
{\large\bf EXECUTION OF DOCUMENTS\par}
\hrulefill
\vspace{5mm}

\section{Execution of Documents}
\begin{subs}
\subsection{Subject to any requirement of the Act or any other law, the President and one other Director of the Board may execute documents on behalf of the Association on Ordinary Resolution of the Board.}
\end{subs}

{\large\bf WINDING UP\par}
\hrulefill
\vspace{5mm}

\section{Winding up}
\begin{subs}
\subsection{The Association may be wound up in the manner provided in the Act.}
\end{subs}

\vspace{5mm}
{\large\bf DISTRIBUTION OF FUNDS AND ASSETS\par}
\hrulefill
\vspace{5mm}

\section{Distribution of Funds and Assets}
\begin{subs}
\subsection{In the event that the Association is wound up:}
\begin{subs}
\subsubsection{Funds and Assets of the Association are not to be distributed to General Members of the Association.}
\subsubsection{All Funds and Assets are to be appropriated and applied in satisfaction of all debts and liabilities of the Association.}
\subsubsection{All Funds and Assets remaining after the satisfaction of all debts and liabilities of the Association are to be distributed amongst existing sponsors; or}
\subsubsection{Be distributed to any other organisation that has similar objects to the Association, upon an Ordinary Resolution of the Board.}
\end{subs}
\end{subs}
\newpage

\vspace{5mm}
{\large\bf ALTERATION TO THE CONSTITUTION\par}
\hrulefill

\section{Alterations to the Constitution}
\begin{subs}
\subsection{The Constitution may be altered at any time by a Special Resolution passed at a general meeting of members the notice whereof refers to a proposed alteration or alterations to the rules of the Association.}
\subsection{The alteration shall be registered with the Corporate Affairs Commission as required by the Act.}
\subsection{The registered rules shall bind the Association and every member to the same extent as if they respectively signed and sealed them, and agreed to be bound by all provisions thereof.}
\subsection{Subject to any provision in the rules or a resolution to the contrary, an alteration to the rules comes into force at the time that the alteration has passed. This does not apply to an alteration to the name of the Association which does not come into force until registered by the Consumer and Business Services, Corporate Services Commission.}

\subsection{Any notice of an amendment to the Association's Constitution must set out:}
\begin{subs}
\subsubsection{The terms of the proposed amendment;}
\subsubsection{The intended effect of the proposed amendment;}
\subsubsection{A statement of whether the proposed amendment complies with the Objectives of the Association currently in force; and}
\subsubsection{Any other matter relevant to the proposed amendment.}
\end{subs}
\end{subs}

\end{document}

